Nail: A practical interface generator for data formats

### 2014-05-02 paper/osdi14/design.tex
Design XXX

\paragraph{Choices.}
Our choice combinator takes multiple labeled parsers and tries each of them in turn, backtracking
to the initial position if an option fails. This behavior for the choice combinator, the defining
feature of Parser Expression Grammars~\cite{ford2002packrat}, resolves any ambiguities explicitly.
Internally, the choice combinator represents choices as tagged unions.

If two options the same string could be parser by two options, generated output for the latter
option is not necessarily understood identically by the parser. However, actual data formats are
usually not ambiguous in this sense.
\XXX[nz][I don't understand this paragraph (esp the first sentence).]

@@

\XXX[nz][Do you need \cc{*} here?  It seems like \cc{optional paren} would
already have a C representation of \cc{paren*} according to our big figure.]

>>>>

\paragraph{Choices.}
If multiple structures can appear at a given position in a format, the programmer lists the options
along with a label for each in the \cc{choose} combinator. 
During parsing, Nail remembers the current input position and attempts each option in the order they
appear in the grammar. If an option fails, the parser backtracks to the initial position. If no
options succeed, the entire combinator fails. In the data model, choices are represented as tagged
unions.  The programmer has to be careful when options overlap, because if the programmer meant to
generate output for a choice, but the external representation is also valid for an earlier,
higher-priority option, the parser will interpret it as such. However, real data formats normally do
not have this overlap and we did not encounter it in the grammars we wrote.

% If two options the same string could be parsed by two options, generated output for the latter
% option is not necessarily understood identically by the parser. However, actual data formats are
% usually not ambiguous in this sense.
% \XXX[nz][I don't understand this paragraph (esp the first sentence).]

@@
